Transfer Learning in Visual and Relational Reasoning

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
Small edits in Model section + move Fig 1 on page 4.

The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell. Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}. Information flows between frames through the external memory.
During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
(a) $\vec{c}_t \in \Reals^d$, the control state used to drive reasoning over objects in the frame and memory; and
(b) $\vec{so}_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
Let $\vec{M}_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
in a trained model, $\whead_t$ points to the location of the first empty slot in memory for adding new objects.

@@

The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
A similar operation on memory yields the object $\vec{mo}_t$. The memory operation is based on attention mechanism, and resembles content-based addressing. Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
%Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.

@@

\noindent{\textbf{Summary Update Unit.}}
%\paragraph{Summary Update Unit.}
This unit updates the (recurrent) summary object to equal the outcome of the $t$-th reasoning step.
We first determine whether the relevant object $\vec{ro}_t$ should be obtained from memory or the frame according to:
\[ \vec{ro}_t = \imatch_t \cdot \vec{vo}_t + \mmatch_t \cdot \vec{mo}_t \]
Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.

>>>>

\noindent{\textbf{The SAM Cell.}} The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell. Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}. Information flows between frames through the external memory.
During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
(a) $\vec{c}_t \in \Reals^d$, the control state used to drive reasoning over objects in the frame and memory; and
(b) $\vec{so}_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
Let $\vec{M}_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
in a trained model, $\whead_t$ points to the location of the first empty slot in memory for adding new objects.

@@

\noindent{\textbf{Retrieval Units.}} The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
A similar operation on memory yields the object $\vec{mo}_t$. The memory operation is based on attention mechanism, and resembles content-based addressing. Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
%Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.

@@

\noindent{\textbf{Summary Update Unit.}}
%\paragraph{Summary Update Unit.}
This unit updates the (recurrent) summary object to equal the outcome of the $t$-th reasoning step.
We first determine whether the relevant object $\vec{ro}_t$ should be obtained from memory or the frame according to:
\[ \vec{ro}_t = \imatch_t \cdot \vec{vo}_t + \mmatch_t \cdot \vec{mo}_t \]
Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.

\noindent{\textbf{Output Unit.}} Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
